\textbf{}\begin{thebibliography}{10}

\frenchspacing
\bibitem{Dirac}
P.A.M. Dirac, \emph{The Principles of Quantum Mechanics}. Clarendon Press, Oxford (1958)

\bibitem{Bransden}
B.H. Bransden e C.J. Joachain, \emph{Physics of Atoms and Molecules}. Prentice Hall (2003)

\bibitem{Krane}
K. S. Krane, \emph{Introductory nuclear physics}. Wiley (1988)

\bibitem{Lee}
T. D. Lee, \emph{Particle Physics and Introduction to Field Theory}. Harwood Academic Publishers (1981)

\bibitem{Kabir}
P. K. Kabir, \emph{The CP puzzle. Strange decays of the neutral Kaon}. Academic Press INC. (1968)

\bibitem{BigiSanda}
I.I. Bigi e A.I. Sanda, \emph{CP Violation}. Cambridge University Press (2008).

\bibitem{Branco}
G. S. Branco, L. Lavoura e J.P. Silva, \emph{CP Violation}. Oxford Science Publication (1999).

\bibitem{Sozzi}
M. S. Sozzi, \emph{Discrete Symmetries and CP Violation}. Oxford University Press (2008).

\bibitem{Kobayashi}
M. Kobayashi, T. Maskawa, \emph{CP-Violation in the Renormalizable Theory of Weak Interaction}. Progress of Theoretical Physics, Vol.49, No. 2 1972.

\bibitem{Wong}
S. Wong, \emph{Introductory Nuclear Physics}. Wiley Interscience, 2nd Ed (1999).

\bibitem{Maiani}
L. Maiani, \emph{Interazioni Elettrodeboli}. Università di Roma ``La Sapienza'' (2012).

\bibitem{d'agostini}
G. D'Agostini, \emph{Bayesian Reasoning in Data Analysis}. World Scientific (2003).

\bibitem{LHCb}
A. Alves et al., \emph{The LHCb detector at the LHC}. Journal of Instrumentation (2008).

\bibitem{Atwood:1996ci}
  D.~Atwood, I.~Dunietz and A.~Soni, Phys.\ Rev.\ Lett.\  {\bf 78} (1997) 3257
  [hep-ph/9612433].

\bibitem{Gronau:1990ra}
  M.~Gronau and D.~London, Phys.\ Lett.\ B {\bf 253} (1991) 483.

\bibitem{Gronau:1991dp}
  M.~Gronau and D.~Wyler,  Phys.\ Lett.\ B {\bf 265} (1991) 172.

\bibitem{Giri:2003ty}
  A.~Giri, Y.~Grossman, A.~Soffer and J.~Zupan,  Phys.\ Rev.\ D {\bf 68} (2003) 054018
  [hep-ph/0303187].

\bibitem{cleo}
  N.~Lowrey {\it et al.}  [CLEO Collaboration], Phys.\ Rev.\ D {\bf 80} (2009) 031105 [arXiv:0903.4853 [hep-ex]].

\bibitem{HFAG}
 Y.~Amhis {\it et al.}  [Heavy Flavor Averaging Group Collaboration], arXiv:1207.1158 [hep-ex].

\bibitem{BaBar}
 Risultatato presentato al \emph{Workshop CKM 2012} \\https://indico.cern.ch/contributionDisplay.py contribId=89$\&$confId=208832.

\bibitem{Belle}
Risultato presentato al \emph{Workshop CKM 2012} \\https://indico.cern.ch/contributionDisplay.py?contribId=90$\&$confId=208832.

\bibitem{LHCBB2}
LHCb collaboration, R. Aaij \emph{et al.}, \emph{Observation of CP violation in} $B^+\rightarrow DK^+$ \emph{decays}, Phys. Lett. \textbf{B712} (2012) 203.

\bibitem{LHCBB3}
LHCb collaboration, R. Aaij \emph{et al.}, \emph{A Model - independent Dalitz plot analysis of} $B^{\pm}\rightarrow DK^{\pm} $, $D\rightarrow K_Sh^+h^-$ ($h = \pi, K$) \emph{decays and constraints on the CKM angle $\gamma$}, LHCb-PAPER-2012-027.

\bibitem{LHCBB4}
LHCb collaboration, \emph{Observation of the suppressed} $B^+\rightarrow [\pi^+, K^-, \pi^+, \pi^-]_D \pi^+$ \emph{and} $B^+\rightarrow [\pi^+, K^-, \pi^+, \pi^-]_D \pi^+$ \emph{decays},  LHCb-CONF-2012-030.


\end{thebibliography}
